In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-20 paper/main.tex
More work on reviewer comments

% Limitations
In terms of limitations, our primary constraint modelling-wise is the
geometric representation of the vascular (and therefore also
perivascular) networks. Concretely, we account for no vessels below
the original MRI resolution limits, and thus only a part of the
cerebral surface vasculature and effectively not the cortical
vessels. In addition, and again due to lack of resolution, there is
uncertainty associated with the location of the vessel segments
relative to the CSF spaces and parenchyma, with some vessels
surrounded by both domains and some vessels completely entering the
parenchyma before returning to the SAS. Higher resolution MRI data
(T1w and e.g. time-of-flight, QSM or other modalities) in more
subjects would immediately allow for more detailed studies of this
aspect. As a result of the lack of an accurate representation of the
cortical and subcortical white matter vasculature, we have considered
a basic transport model within the parenchyma, modelling extracellular
diffusion alone. To compensate, we have focused on reporting detailed
predictions in the CSF spaces and surface PVS after not more than 24
hours. In particular, we note that, we observe tracer accumulation at
the perivascular network ends after 12 hours, similar to that
previously observed for microspheres~\cite{bedussi2018paravascular,
  mestre2018flow}, which here can be interpreted as an artifact of the
incomplete network creating a barrier for tracer movement. Previously,
by inferring transport parameters within the human brain from
glymphatic MRI data, we have found that molecular transport within the
parenchyma is well-represented by $\approx 3\times$ enhanced diffusion
augmented by local clearance e.g.~across the blood-brain barrier, or
by diffusion-convection with a complex pattern of spatially-varying
interstitial fluid flow on the order of 1-10 \textmu
m/min~\cite{vinje2023human}. We will incorporate such transport
mechanisms within the parenchyma in future work. Finally, we also note
that we simulate the intracranial distribution of a tracer
concentration appearing at the craniocervical junction rather than as
an intrathecal injection. We thus neglect absorption of both CSF and tracer in the spinal compartment, and therefore overestimate the amount of
tracer entering into the intracranial spaces; however, due to the
linearity of the mathematical model, it is valid to directly interpret
the in-silico concentrations relative to the total amount of tracer.

% Outlook
In conclusion, our findings transfer insights from experimental
studies and theoretical analysis to the in-silico human setting,
reconcile seemingly conflicting observations in particular relating to
directionality of perivascular flow, and integrate different physical
mechanisms across spatial and temporal scales. The complete
simulation pipeline is openly available, including interactive
visualization of simulation results for all model
variations~\cite{ZENODO}. Looking ahead, this platform establishes a
foundation for in-silico studies of molecular movement within the
human brain environment, such as tailored predictions of intrathecal
chemotherapy delivery or personalized diagnostics of brain clearance
capacity.

>>>>

% Limitations
In terms of limitations, our primary constraint modelling-wise is the
geometric representation of the vascular (and therefore also
perivascular) networks. Concretely, we account for no vessels below
the original MRI resolution limits, and thus only a part of the
cerebral surface vasculature and effectively not the cortical
vessels. In addition, and again due to lack of resolution, there is
uncertainty associated with the location of the vessel segments
relative to the CSF spaces and parenchyma, with some vessels
surrounded by both domains and some vessels completely entering the
parenchyma before returning to the SAS. Higher resolution MRI data
(T1w and e.g. time-of-flight, QSM or other modalities) in more
subjects would immediately allow for more detailed studies of this
aspect. As a result of the lack of an accurate representation of the
cortical and subcortical white matter vasculature, we have considered
a basic transport model within the parenchyma, modelling extracellular
diffusion alone and no bulk interstitial fluid flow. To compensate, we
have focused on reporting detailed predictions in the CSF spaces and
surface PVS after not more than 24 hours. In particular, we note that,
we observe tracer accumulation at the perivascular network ends after
12 hours, similar to that previously observed for
microspheres~\cite{bedussi2018paravascular, mestre2018flow}, which
here can be interpreted as an artifact of the incomplete network
creating a barrier for tracer movement. Previously, by inferring
transport parameters within the human brain from glymphatic MRI data,
we have found that molecular transport within the parenchyma is
well-represented by $\approx 3\times$ enhanced diffusion augmented by
local clearance e.g.~across the blood-brain barrier, or by
diffusion-convection with a complex pattern of spatially-varying
interstitial fluid flow on the order of 1-10 \textmu
m/min~\cite{vinje2023human}. We will incorporate such transport
mechanisms within the parenchyma in future work. Finally, we also note
that we simulate the intracranial distribution of a tracer
concentration appearing at the craniocervical junction rather than as
an intrathecal injection. We thus neglect absorption of both CSF and
tracer in the spinal compartment, and therefore overestimate the
amount of tracer entering into the intracranial spaces; however, due
to the linearity of the mathematical model, it is valid to directly
interpret the in-silico concentrations relative to the total amount of
tracer.

% Outlook
In conclusion, our findings transfer insights from experimental
studies and theoretical analysis to the in-silico human setting,
reconcile seemingly conflicting observations in particular relating to
directionality of perivascular flow, and integrate different physical
mechanisms across spatial and temporal scales. The complete simulation
pipeline is openly available, including interactive visualization of
simulation results for all model variations~\cite{ZENODO}. Future work
will focus on further model validation including comparisons between
in-silico predictions and glymphatic MRI for a number of subjects
across several patient cohorts. Looking ahead, this platform
establishes a foundation for in-silico studies of molecular movement
within the human brain environment, such as tailored predictions of
intrathecal chemotherapy delivery or personalized diagnostics of brain
clearance capacity.
